Fisher's method tables and plots

### 2020-05-19 Fishers_method/Fishers method tables and plots.Rmd
previously uncommitted changes to Fisher's method

study_labels <- c( 'RPE' = "RPE, k = 7", 'RPP' = "RPP, k = 64")

plot_all <- ggplot(RPP_RPE_power_results, aes(x = prop, y = power, color = factor(delta)))+
  facet_grid(rows = vars(study), labeller = labeller(study = study_labels)) +
  stdtheme +
  theme(strip.text = element_text(size = 16))+
  scale_x_continuous(name = "Proportion of false negatives") +
  scale_y_continuous(name = "Power")+
  labs(color = expression(delta))+
  geom_line()
plot_all
```

@@

all <- rbind(k10,k50,k100)
plot_general_case <- ggplot(all, aes(x = prop, y = power, color = factor(delta))) +
  facet_grid(k~n, labeller = labeller(n = n_labels, k = k_labels)) +
  stdtheme + 
  theme(axis.text = element_text(size = 6), strip.text = element_text(size = 16)) +
  scale_x_continuous(name = "Proportion of false negatives" ) +
  scale_y_continuous(name = "Power") +
  labs(color = expression(delta))+
  geom_line()

plot_general_case
```

>>>>

study_labels <- c( 'RPE' = "RPE, r = 7", 'RPP' = "RPP, r = 64")

plot_all <- ggplot(RPP_RPE_power_results, 
                   aes(x = prop, y = power, linetype = factor(delta)))+
  facet_grid(rows = vars(study), labeller = labeller(study = study_labels)) +
  stdtheme +
  theme(strip.text = element_text(size = 16))+
  scale_x_continuous(name = "Proportion of false negatives") +
  scale_y_continuous(name = "Power of Fisher's method")+
  labs(linetype = expression(delta))+
  geom_line()
plot_all

plot_worst <- ggplot(RPP_RPE_worst, aes(x = prop, y = power, linetype = factor(delta)))+
  facet_grid(rows = vars(study), labeller = labeller(study = study_labels)) +
  stdtheme +
  theme(strip.text = element_text(size = 16))+
  scale_x_continuous(name = "Proportion of false negatives") +
  scale_y_continuous(name = "Power of Fisher's method")+
  labs(linetype = expression(delta))+
  geom_line()
plot_worst
```

@@

all <- rbind(k10,k50,k100)
plot_general_case <- ggplot(all, aes(x = prop, y = power, linetype = factor(delta))) +
  #facet_grid(k~n, labeller = labeller(n = n_labels, k = k_labels)) +
  stdtheme + 
  theme(axis.text = element_text(size = 6), strip.text = element_text(size = 16)) +
  scale_x_continuous(name = "Proportion of false negatives" ) +
  scale_y_continuous(name = "Power") +
  labs(linetype = expression(delta))+
  geom_line()

plot_general_case

power_80_k10 <- dplyr::filter(all, k == 10 & ((delta == .8 & n == 25 ) | (delta == 0.5 & (n == 50 | n == 75)) | (delta == 0.2 & n == 100)))

```
